---
title: "FM2"
author: "Vijay"
date: '2022-21-02'
output:
  pdf_document: default
  word_document: default
  html_document: default
---

```{r}
getwd()
```

##Here I am Importing the Dataset
```{r}
bank.df= read.csv("universalBank.csv")
```

```{r}
summary(bank.df)
```

```{r}
library(caret)
library(class)
library(dplyr)
library(ISLR)
library(psych)
library(FNN)
library(lattice)
```

##Now I am going to Remove ID ,  ZIP Code 
```{r}
bank.df$ID <- NULL
bank.df$ZIP.Code <- NULL
bank.df$Education = as.factor(bank.df$Education)
```

##later I am creating a dummy dataset
```{r}
dummyvari <- as.data.frame(dummy.code(bank.df$Education))
```

```{r}
names(dummyvari) <- c("Education_1", "Education_2","Education_3")
```

##Now I am setting  education to NULL
```{r}
bank.df$Education <- NULL
```

```{r}
bank_Final <- cbind(bank.df, dummyvari)

```

##Here I am going to divide the dataset into train and test
```{r}
set.seed(1)
train.index <- createDataPartition(bank_Final$Personal.Loan, p= 0.6 , list=FALSE)
valid.index <- setdiff(row.names(bank_Final), train.index)
train.df <- bank_Final[train.index,]
valid.df <- bank_Final[valid.index,]
```

##Now we are generating the Test data
```{r}
new_customer <- data.frame(Age = 40,
                       Experience = 10,
                       Income = 84,
                       Family = 2,
                       CCAvg = 2,
                       Mortgage = 0,
                       Securities.Account = 0,
                       CD.Account = 0,
                       Online = 1,
                       CreditCard = 1,
                       Education_1 = 0, 
                       Education_2 = 1, 
                       Education_3 = 0)
                       
```
## normalisation
```{r}
train.norm.df <- train.df[,-7]
valid.norm.df <- valid.df[,-7]
new_customer.norm <- new_customer

norm.values <- preProcess(train.df[, -7], method=c("center", "scale"))
train.norm.df <- predict(norm.values, train.df[, -7])
valid.norm.df <- predict(norm.values, valid.df[, -7])
new_customer.norm <- predict(norm.values, new_customer.norm)
```

```{r}

summary(train.norm.df)

```
##Here I am Performing Knn classification, using K=1
```{r}

outputrate <- class::knn(train = train.norm.df,test = new_customer.norm,
                       cl = train.df$Personal.Loan, k = 1)

print(outputrate)
```


##we are going to find best K
```{r}
accuracy.df <- data.frame(k = seq(1, 10, 1), accuracy = rep(0, 10))
```


```{r}
for(i in 1:10) {
  knn.prediction <- class::knn(train = train.norm.df,
                         test = valid.norm.df,
                         cl = train.df$Personal.Loan, k = i)
  accuracy.df[i, 2] <- confusionMatrix(knn.prediction,
                                       as.factor(valid.df$Personal.Loan))$overall[1]
}
which(accuracy.df[,2] == max(accuracy.df[,2]))
```


```{r}
accuracy.df
```



##choosing k = 3
```{r}
knn.prediction <- class::knn(train = train.norm.df,
                       test = valid.norm.df,
                       cl = train.df$Personal.Loan, k = 3)

confusionMatrix(knn.prediction, as.factor(valid.df$Personal.Loan), positive = "1")
```

##Now Here confusion matrix for the best k value =3

```{r}
newcustomer <- data.frame(Age = 40,
                            Experience = 10,
                            Income = 84,
                            Family = 2,
                            CCAvg = 2,
                            Mortgage = 0,
                            Securities.Account = 0,
                            CD.Account = 0,
                            Online = 1,
                            CreditCard = 1,
                            Education_1 = 0, 
                            Education_2 = 1, 
                            Education_3 = 0)

fitknn <-class::knn(train = train.norm.df,
                          test = newcustomer,
                          cl = train.df$Personal.Loan, k = 3)

fitknn
```
##knn model tells that new customer will accept loan
##reading the dataset

```{r}
bank.df= read.csv("universalBank.csv")
```

##packages

```{r}
library(ISLR)
library(psych)
library(caret)
library(FNN)
library(class)
library(dplyr)
library(lattice)

```

##here i am removing id and zipcode variables from the dataset

```{r}
bank.df$ID <- NULL
bank.df$ZIP.Code <- NULL
bank.df$Education = as.factor(bank.df$Education)

```

##Creating a dummy dataframe

```{r}
dummymod <- as.data.frame(dummy.code(bank.df$Education))

```

##Renaming the data frame

```{r}
names(dummymod) <- c("Education_1", "Education_2","Education_3")

```

##deleting education variable

```{r}
bank.df$Education <- NULL 

```

##Main dataset

```{r}
bank_Final <- cbind(bank.df, dummymod)

```

#Partitioning  the dataset

```{r}
set.seed(1)
train.index <- createDataPartition(bank_Final$Personal.Loan, p= 0.5 , list=FALSE)
valid.index <- createDataPartition(bank_Final$Personal.Loan, p= 0.3 , list=FALSE)
test.index <- setdiff(row.names(bank_Final), union(train.index, valid.index))
                      
train.df <- bank_Final[train.index, ]
valid.df <- bank_Final[valid.index, ]
test.df <- bank_Final[test.index, ]

```

##Performing normalisation

```{r}
train.norm.df <- train.df[,-7]
valid.norm.df <- valid.df[,-7]
test.norm.df <- test.df[,-7]

norm.values <- preProcess(train.df[, -7], method=c("center", "scale"))
train.norm.df <- predict(norm.values, train.df[, -7])
valid.norm.df <- predict(norm.values, valid.df[, -7])
test.norm.df <- predict(norm.values, test.df[, -7])

```

##Performing Knn classification using K=3

```{r}
knn.test.pred <- class::knn(train = train.norm.df,
                       test = test.norm.df,
                       cl = train.df$Personal.Loan, k = 3)

knn.train.pred <- class::knn(train = train.norm.df,
                             test = train.norm.df,
                             cl = train.df$Personal.Loan, k = 3)

knn.valid.pred <- class::knn(train = train.norm.df,
                             test = valid.norm.df,
                             cl = train.df$Personal.Loan, k = 3)
```

##Confusion matrix for K=3

```{r}
confusionMatrix(knn.test.pred, as.factor(test.df$Personal.Loan), positive = "1")
confusionMatrix(knn.train.pred, as.factor(train.df$Personal.Loan), positive = "1")
confusionMatrix(knn.valid.pred, as.factor(valid.df$Personal.Loan), positive = "1")

```
