---
title: "FML5"
author: "Vijay"
date: '2022-04-16'
output: pdf_document
---
```{r}
# installing required packages
library(ISLR)
library(caret)
library(dplyr)
library(factoextra)
library(ggplot2)
library(proxy)
library(tidyverse)
library(cluster)
library(NbClust)
library(ppclust)
library(dendextend)
```

```{r}
# Importing cereal dataset
cereals <- read.csv("cereals.csv")
## Reviewing the Dataset
# Reviewing first five rows of the dataset
head(cereals)
# checking the structure of the dataset
str(cereals)
# summary of the dataset
summary(cereals)
```

The data has to be scaled before  removing the NA values from the data set.
```{r}
# Creating duplicate dataset for preprocessing
cereal_data <- cereals
# Scale the dataset before placing that into a clustering algorithm
cereal_data[ , c(4:16)] <- scale(cereals[ , c(4:16)])
# Removing Null values from dataset
cereal_pre <- na.omit(cereal_data)
# Review the first five rows of scaled data set after removing Null values
head(cereal_pre)
```
After preprocessing 3 null values have been found in the dataset

## Q) Apply hierarchical clustering to the data using Euclidean distance to the normalized measurements. Use Agnes to compare the clustering from  single linkage, complete linkage, average linkage, and Ward. Choose the best method.

# Single Linkage:
```{r}
# Creating dissimilarity matrix for the numeric values in the dataset using Euclidean distance
cereal_EUC <- dist(cereal_pre[ , c(4:16)], method = "euclidean")
# Performing hierarchical clustering using single linkage
agnes_hc_single <- agnes(cereal_EUC, method = "single")
# Plot the results of the different methods
plot(agnes_hc_single, 
     main = "Single Linkage Method",
     xlab = "Cereal",
     ylab = "Height",
     cex.axis = 1,
     cex = 0.50)
```

# Complete Linkage:
```{r}
# Performing hierarchical clustering using complete linkage method
agnes_hc_complete <- agnes(cereal_EUC, method = "complete")
# Plot the results of the different methods
plot(agnes_hc_complete, 
     main = "Complete Linkage Method",
     xlab = "Cereal",
     ylab = "Height",
     cex.axis = 1,
     cex = 0.50)
```

# Average Linkage:
```{r}
# Performing hierarchical clustering using average linkage method
agnes_hc_average<- agnes(cereal_EUC, method = "average")
# Plot the results of the different methods
plot(agnes_hc_average, 
     main = "Average Linkage Method",
     xlab = "Cereal",
     ylab = "Height",
     cex.axis = 1,
     cex = 0.50)
```

# Ward Method:
```{r}
# Performing hierarchical clustering using ward linkage method
agnes_hc_ward <- agnes(cereal_EUC, method = "ward")
# Plot the results of the different methods
plot(agnes_hc_ward, 
     main = "Ward Linkage Method",
     xlab = "Cereal",
     ylab = "Height",
     cex.axis = 1,
     cex = 0.50)
```
Based on the agglomerative coefficient the best clustering method is that which returned from the each method The close the value is to 1.0, the closer the clustering structure will be. So, the method with the value closer to 1.0 will be chosen

Single Linkage: 0.61
Complete Linkage: 0.84
Average Linkage: 0.78
Ward Method: 0.90

The Ward method will be chosen as the best clustering model based on the result.

## Q) How many clusters would you choose? 

# To determine Appropriate number of Clusters we use the elbow method and silhouette method.

# Elbow Method:
```{r}
# To Determine the optimal number of clusters using the Elbow method
fviz_nbclust(cereal_pre[ , c(4:16)], hcut, method = "wss", k.max = 25) +
  labs(title = "Optimal No of Clusters - Elbow Method") +
  geom_vline(xintercept = 12, linetype = 2)
```

# Silhouette Method:
```{r}
# Determine the optimal number of clusters for the dataset via the silhouette method
fviz_nbclust(cereal_pre[ , c(4:16)], 
                               hcut, 
                               method = "silhouette", 
                               k.max = 25) +
  labs(title = "Optimal No. of Clusters - Silhouette Method")
```
Based on the results of the elbow and silhouette methods, the number of clusters are 12.

Outline the 12 clusters on the hierarchical tree
```{r}
# Plot of the Ward hierarchical tree with the 12 clusters outlined for reference
plot(agnes_hc_ward, 
     main = "AGNES - Ward Linkage Method",
     xlab = "Cereal",
     ylab = "Height",
     cex.axis = 1,
     cex = 0.50,)
rect.hclust(agnes_hc_ward, k = 12, border = 1:12)
```

Q) The elementary public schools would like to choose a set of cereals to include in their daily cafeterias. Every day a different cereal is offered, but all cereals should support a healthy diet. For this goal, you are requested to find a cluster of “healthy cereals.” Should the data be normalized? If not, how should they be used in the cluster analysis? 

Ans:Normalizing the data is not a good idea in this situation because of Nutritional information of cereals is normalized based on cereal evaluated so the collected data can only has cereals with high sugar quantity and less iron,fiber and other nutrition data. so its not possible to tell nourishment the ceral provides to a child once its normalized thoughout sample.we may infer that a cereal with iron quantity of 0.99 means it is sufficient for a child yet,it simply have no nutritional value. As a result, a best way to preprocess the data would be to convert it to a ratio of daily recommended calories, fiber, carbohydrates, and other nutrients for a child. This makes analysts to take more informed decisions on clusters during reviewing and also preventing a few larger variables from overriding the distance estimates. By looking at the clusters the analyst may have to look at the cluster average to see what percentage of a student's daily required nutrition that would come from cereal.
